Exploring Factors Influencing Average Playtime of Video Games: A Regression Analysis

### 2024-12-04 paper/paper.Rmd
Edited the introduction to increase elegance and clarity, and added editing process document.

The gaming industry has experienced exponential growth in recent years,
with millions of players engaging in various games on platforms like
Steam. Understanding what influences average playtime in games is
crucial for game developers, publishers, and marketers. Average playtime
is a key indicator of player engagement and game success, and
investigating factors that impact it can provide valuable insights into
game design, pricing strategies, and marketing efforts. So our research
aims to explore the factors that influence the average playtime of games
available on Steam using a dataset we get from Kaggle. Specifically, we
will investigate how variables such as price, user ratings, and other
game characteristics contribute to player engagement, as measured by
playtime. From some previous papers, we learned that both positive and
negative reviews have a significant correlation with playtime, but the
effect is more pronounced for positive reviews [@paper1]. Another paper
found out that game pricing significantly affects player engagement,
with lower-priced games generally seeing higher playtime [@paper2]. The
third paper did an empirical study that also examined the influence of
game reviews on playtime, focusing on how the number and sentiment of
reviews can affect player engagement. It concludes that games with more
positive reviews see increased playtime, especially if those reviews
highlight the game’s quality [@paper3]. We found this problem suitable
for linear regression because it allows us to model the relationship
between average playtime (the dependent variable) and various predictors
(price, ratings, developer, etc.). This approach helps quantify how each
factor influences playtime, enabling a clear understanding of the impact
of different game attributes. By fitting a linear regression model, we
can determine which factors have statistically significant effects on
playtime, providing actionable insights for game developers and
marketers.

>>>>

The gaming industry has experienced remarkable growth in recent years, with millions of players engaging on platforms like Steam. Understanding the factors that influence average playtime is crucial for developers, publishers, and marketers alike. As a key indicator of player engagement and game success, playtime can offer valuable insights into game design, pricing, and marketing strategies. Our research aims to explore the factors that affect the average playtime of games on Steam, using a dataset sourced from Kaggle. Specifically, we will examine how variables such as price, user ratings, and other game attributes contribute to player engagement. Previous studies have shown that both positive and negative reviews correlate with playtime, though the effect of positive reviews is more pronounced [@paper1]. Additionally, research suggests that pricing plays a significant role, with lower-priced games generally seeing higher playtime [@paper2]. Another study highlighted the influence of review sentiment, concluding that games with more positive reviews tend to have increased playtime, especially when those reviews emphasize game quality [@paper3]. We have chosen linear regression to model the relationship between playtime (the dependent variable) and various predictors, such as price and ratings. This approach will quantify how each factor impacts playtime, providing clear insights into the influence of game attributes. By fitting this model, we aim to identify the factors with statistically significant effects on playtime, offering actionable recommendations for developers and marketers.
